---
title: "Load data from multiple Excel worksheets"
author: "Reed College, Instructional Technology Services"
output: html_document
---
<BR>
<BR>

#### Introduction
The following code allows you to read in data from each page of an Excel workbook into a list of data frames in R. Then the code will run a function to clean the data in each of those data frames. Lastly, the data frames are joined together into one data frame for analysis. 

<BR>

#### Install and Load XLConnect Package
```{r, eval=FALSE}

# install and load packages -----------------------------------------------
pkg <- c("XLConnect")

new.pkg <- pkg[!(pkg %in% installed.packages())]

if (length(new.pkg)) {
  install.packages(new.pkg)
}

library(XLConnect)

```

<BR>

#### Read in Data from Excel Worksheets
```{r, eval=FALSE}

# load excel workbook
excel <- loadWorkbook("filepath/ExcelData.xlsx") # change to match your path

# get sheet names
sheet_names <- getSheets(excel)
names(sheet_names) <- sheet_names

# put sheets into a list of data frames
sheet_list <- lapply(sheet_names, function(.sheet){readWorksheet(object=excel, .sheet)})

# limit sheet_list to sheets with at least 1 dimension 
sheet_list2 <- sheet_list[sapply(sheet_list, function(x) dim(x)[1]) > 0]
```

<BR>

#### Define and Run Function to Clean Data
```{r, eval=FALSE}

# code to read in each excel worksheet as individual dataframes
# for (i in 2:length(sheet_list2)){assign(paste0("df", i), as.data.frame(sheet_list2[i]))}

# define function to clean data in each data frame (updated based on your data)
cleaner <- function(df){
  # drop rows with missing values 
  df <- df[rowSums(is.na(df)) == 0,] 
  # remove serial comma from all variables 
  df[,-1] <- as.numeric(gsub(",", "", as.matrix(df[,-1])))
  # create numeric version of year variable for graphing 
  df$Year <- as.numeric(substr(df$year, 1, 4))
  # return cleaned df      
  return(df)
}

# clean sheets and create one data frame
# data <- do.call(rbind,lapply(seq_along(sheet_list2), function(x) cleaner(sheet_list2[[x]])))
data <- do.call(rbind,lapply(names(sheet_list2), function(x) cleaner(sheet_list2[[x]])))


```


