---
title: "Geocoder & Coordinate Conversion"
author: "Rich Majerus & Kristin Bott"
date: "March 4, 2015"
output: html_document
---
<br/>  

### Intro 
Some introductory text could go here....    

<br/>  
  

A word about packages here...

```{r, warning=FALSE}
library(stringr)
library(httr)
library(rjson)
suppressMessages(library(dplyr))
#library(devtools)
#if (!require("leaflet")) devtools::install_github("rstudio/leaflet")
library(leaflet)
```

<br/>

### Geocoding function...
Some text about geocoding function here  

<br/>

```{r, echo=FALSE}

# create geocode function with tryCatch for errors
geo.dsk <- function(addr){ 
  require(httr)
  require(rjson)
  
  out <- tryCatch({
  
  url      <- "http://www.datasciencetoolkit.org/maps/api/geocode/json"
  response <- GET(url,query=list(sensor="FALSE",address=addr))
  json <- fromJSON(content(response,type="text"))
  loc  <- json['results'][[1]][[1]]$geometry$location
  return(c(address=addr,long=loc$lng, lat= loc$lat))
  }, 
    
  error = function(cond) {
            message(paste("Address not geocoded:", addr))
            message("Here's the original error message:")
            message(cond)
            # Choose a return value in case of error
            return(NA)
        },  

 warning = function(cond) {
            message(paste("Address caused a warning:", addr))
            message("Here's the original warning message:")
            message(cond)
            # Choose a return value in case of warning
            return(NULL)
        },

 finally = {
            message(paste("Processed Address:", addr))
            message("One down...")
        }
    )    
    return(out)
}


```

<br/>

Here is an example...

<br/>

```{r}

geo.dsk("Reed College, Portland, OR")

```


<br/>

This works on data frames too!!

<br/>

```{r}

name   <- c('Carleton College', 'Pomona College', 'Reed College')
street <- c('300 North College St', '333 N College Way', '3203 SE Woodstock Blvd') 
city   <- c("Northfield", "Claremont", "Portland") 
state  <- c('MN', 'CA', 'OR') 
zip    <- c('55057', '91711', '97202')

data   <- data.frame(name, street, city, state, zip)      


# create location variable 

data$location <- paste(str_trim(as.character(data$street)),
                       str_trim(as.character(data$city)),
                       str_trim(as.character(data$state)),
                       str_trim(as.character(data$zip)), sep=' ')


# geocode data and bind coordinates onto data

result <- cbind(name= data$name,
                as.data.frame(do.call(rbind,
                              lapply(as.character(data$location), geo.dsk))))

print(result)

```


<br/>

### Coordinate Conversion function...

If we want these data frames in another coordinate system we can simply convert them...

<br/>

```{r}

# coordinate conversion function 
degrees2meters = function(lon, lat) {
  x = lon * 20037508.34 / 180;
  y = log(tan((90 + lat) * pi / 360)) / (pi / 180);
  y = y * 20037508.34 / 180;
  z <- paste('POINT(', x,' ', y, ')', sep='')
  return(z)
}



```

<br/>
Here is the first example converted....
<br/>

```{r}

# coordinate conversion function 
degrees2meters = function(lon, lat) {
  x = lon * 20037508.34 / 180;
  y = log(tan((90 + lat) * pi / 360)) / (pi / 180);
  y = y * 20037508.34 / 180;
  z <- paste('POINT(', x,' ', y, ')', sep='')
  return(z)
}


degrees2meters(-122.629179, 45.479171)


```

<br/>
This will work on data frames too! 
<br/>

```{r}

result.converted <- cbind(name = result$name,
                          as.data.frame(mapply(degrees2meters, as.numeric(result$long), as.numeric(result$lat))))

colnames(result.converted) <- c('name', 'coords')


print(result.converted)


```
<br/>

### Last Step...make a map

<br/>
```{r}

# create map

leaflet(result) %>%
  addTiles() %>%
  setView(-93.65, 42.0285, zoom = 3) %>%
  addCircles(result$long, result$lat) %>%
  addPopups(result$long, result$lat, paste(result$name, '!', sep=''))


```





