---
title: "Histograms in R"
author: "Reed College, Instructional Technology Services"
output: pdf_document
---

**Create Histogram  using Base R Commands**
```{r}
cars <- mtcars
hist(cars$mpg)
```
\newpage

**Add Additional Elements to Base Histogram**
```{r}
hist(cars$mpg,
     xlab = "MPG", ylab = "Frequency",  main = "Histogram of MPG", # Add labels
     breaks=12,  # set number of bins
     col = "dark blue") # change color 


```
\newpage

**Create Kernal Density using Base R Commands**
```{r}
plot(density(cars$mpg))

```
\newpage

**Add Additional Elements to Base Density Plot**
```{r}
plot(density(cars$mpg),
     xlab = "MPG", ylab = "Density",  main = "Density Plot of MPG", # Add labels
     col = "dark blue", lwd = 4) # change color and width of line

```
\newpage

**Using ggplot2 to Make a Histogram**
```{r, message=FALSE}
# This demo requires the 'ggplot' package 
if( !is.element("ggplot2", installed.packages()[,1]) )
  install.packages("ggplot2")

suppressPackageStartupMessages(library(ggplot2))

## Base histogram plot in ggplot 
ggplot(cars, aes(x=mpg)) + geom_histogram()
```
\newpage


**Apply Theme to  Histogram Plot**
```{r, message=FALSE}
ggplot(cars, aes(x=mpg)) + 
  geom_histogram() +
  theme_classic()
```
\newpage

**Add Additional Elements to Histogram**
```{r, message=FALSE}

ggplot(cars, aes(x=mpg)) + 
  geom_histogram(color="dark blue", size=1, fill="light blue", binwidth=15) +  # change color and adjust bindwidth
  ggtitle("Histogram of MPG") + # add a title to the plot 
  theme_classic()

```
\newpage

**Using ggplot to Make a Density Plot**
```{r}

ggplot(cars, aes(x=mpg)) + 
  geom_density(color="dark blue", size=1, fill="light blue") + # change to geom_density for density plot 
  ggtitle("Kernal Density of MPG") + 
  theme_classic()

```
\newpage


