---
title: "Markdown Formatting"
date: Reed College, Instructional Technology Services
output: html_document
---
<br> <br> 

#### **Bold Text**
```{r}
# **text** or __text__ makes your text between the ** or __ bold 
```
For example, __this is bold text that I made using two underscores__  
<br> <br> 

#### *Italic Text*
```{r}
# *text* or _text_ makes your text between the * or _ italic 
```
For example, _this is italic text that I made using one underscore_  
<br> <br> 

#### Line breaks
```{r}
# You can include a line break by ending a line with two (or more) spaces and a return.
# Alternatively, you can use html <br> 
# If we put atwo (or more) spaces and a return after the comma in the preceeding example we get the following: 
```
For example,  
_this is italic text that I made using one underscore_
<br> <br> 


#### Inline R Code
```{r}
# You can insert R code and calculations directly into your text 
# For example, the following line outside of a code chunk is displayed below. 
# The average mpg for cars in the data set is `r round(mean(mtcars$mpg), 2)` miles per gallon.  
```

The average mpg for cars in the data set is `r round(mean(mtcars$mpg), 2)` miles per gallon.  
<br> <br> 


#### Page Breaks 
In html documents you will not need page breaks.  W
```{r}
# When you are producing html documents, you can use the latex command "\pagebreak" to insert a page break
```
<br> <br> 


#### Headings
```{r}
# You can create headings with "#"
# The following text starts with #Heading and ends with ######Heading

```
  
# Heading
## Heading
### Heading
#### Heading
##### Heading
###### Heading
<br> <br> 

