---
title: "Scatter Plots"
author: "Reed College, Instructional Technology Services"
output: html_document
---

<br>
<br>

####Create Data Frame of Majors and FTE by Department at Reed College
```{r}

Departments = c('Art' , 'Music', 'Theatre', 'Anthropology', 'Economics',
                'History', 'Political Science', 'Sociology', 'Chinese',  'Classics',
                'English', 'French', 'German', 'Russian', 'Spanish',
                'Biology', 'Chemistry', 'Mathematics', 'Physics', 'Linguistics',
                'Philosophy', 'Psychology', 'Religion')

Majors = c(58, 21, 16, 52, 56,
          57, 68, 28, 6, 20, 
          150, 5, 2, 7, 3, 
          153.5, 74, 72.5, 125, 45,
          75, 98, 25)

FTE = c(7.8, 4, 6.25, 5, 5.6, 
        8.7, 5.5, 3, 3, 4, 
        12, 5, 3, 3, 5, 
        9, 6.8, 8, 6, 4, 
        5.7, 7.7, 4)

data <- data.frame(Departments, Majors, FTE)

# Data does not include 94 interdisciplinary majors and 40 undecided majors.  
# Majors like bio/chem are split between the two departments 
# General Lit majors are included with English 
# Dance majors and faculty are included with Theatre
# Major Data: http://www.reed.edu/ir/ir_internal_web/intendedmajors.html and FTE Data: http://www.reed.edu/ir/facfte.html

```

<br>
<br>

####Create Scatter Plot using Base R Commands
```{r}
plot(data$Majors, data$FTE)
```

<br>
<br>

####Add Additional Elements to Base Scatter Plot
```{r}
plot(data$Majors, data$FTE, 
     xlab = "Majors", ylab = "FTE",  main = "Reed College Majors and FTE by Deparment ", pch = 16, # Add labels
     xlim = c(0, 160), ylim = c(0, 15),  # set limits on x-axis and y-axis
     col = "dark blue", cex = 2) # change color and size of points


```

<br>
<br>


####Add A Fitted Line
```{r}
plot(data$Majors, data$FTE, 
     xlab = "Majors", ylab = "FTE",  main = "Reed College Majors and FTE by Deparment", pch = 16, # Add labels
     xlim = c(0, 160), ylim = c(0, 15),  # set limits on x-axis and y-axis
     col = "dark blue", cex = 2) # change color and size of points

abline(lm(data$FTE~data$Majors), col="dark red", lwd = 2)  # add fitted regression line (y~x) 

```


<br>
<br>


####Using ggplot2 to Make a Scatter Plot
```{r}
# This demo requires the 'ggplot' package 
if( !is.element("ggplot2", installed.packages()[,1]) )
  install.packages("ggplot2")

suppressPackageStartupMessages(library(ggplot2))

## Base scatter plot in ggplot 
ggplot(data, aes(x=Majors, y=FTE)) + 
  geom_point(shape=1)

```


<br>
<br>

####Apply Theme to  Scatter Plot
```{r}
ggplot(data, aes(x=Majors, y=FTE)) + 
  geom_point(shape=1)+
  theme_bw()



```

<br>
<br>

####Add Additional Elements to Base Scatter Plot
```{r}
ggplot(data, aes(x=Majors, y=FTE)) +  
  geom_point(color="dark blue", size=3) +   # change the color and size of points 
  geom_smooth(method=lm, se=FALSE, color="dark red") + # add a fitted line 
  scale_y_continuous(limits = c(0, 12)) + # apply limits to the y-axis
  ggtitle("Reed College Majors and FTE by Deparment") + # add a title to the plot 
  theme_bw()


```

<br>
<br>

####Make Your Scatter Plot Interactive with googleVis
 
```{r, warning=FALSE}
## This demo requires the 'googleVis' package 
if( !is.element("googleVis", installed.packages()[,1]) )
  install.packages("googleVis")

suppressPackageStartupMessages(library(googleVis))

# make a new data frame with only two columns to scatter plot 
keep <- c('Majors', 'FTE')
data2 <- data[keep]

# add names to new data frame as factor 
data2$pop.html.tooltip=data$Departments

# create interactive scatter plot using googleVis
Scatter1 <- gvisScatterChart(data2,                                                           
                            options=list(tooltip="{isHtml:'True'}",              # Define tooltip                            
                              legend="none", lineWidth=0, pointSize=5,                                                     
                              vAxis="{title:'Faculty (Total FTE)'}",             # y-axis label                
                              hAxis="{title:'Majors (delared and intended)'}",   # x-axis label                     
                              width=750, height=500))                            # plot dimensions                                              
```

```{r, results = 'asis'}
# plot interactive scatter (use 'plot(Scatter1)' to view in RStudio)
print(Scatter1, 'chart') 

```


<br>
<br>


####Add Additional Elements to Interactive Scatter Plot
```{r, warning=FALSE}

# create interactive scatter plot using googleVis
Scatter2 <- gvisScatterChart(data2,                                                           
                            options=list(
                              explorer="{actions: ['dragToZoom', 
                                          'rightClickToReset'],
                                           maxZoomIn:0.05}",
                              #chartArea="{width:'85%',height:'80%'}",
                              tooltip="{isHtml:'True'}",              
                              crosshair="{trigger:'both'}",                         
                              legend="none", lineWidth=0, pointSize=5,                                                     
                              vAxis="{title:'Faculty (Total FTE)'}",                        
                              hAxis="{title:'Majors (delared and intended)'}",                     
                              width=750, height=500))                                                                        
```


```{r, results = 'asis'}
print(Scatter2, 'chart') 

```

Left-click and drag to select an area of the chart to zoom-in on. 
  
